Supporting Information : Effect of copula on extinction risk

### 2019-02-27 SuppMat.Rmd
minor edit

    ricker_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    ricker_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

@@

  plot(ss$d,s$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  liness(s$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
  #---------------------------------------------------
  ## Allow a second plot on the same graph
  #par(new=TRUE)

>>>>

    ricker_extrisk_d0$risk_left_d0[i]<-ss$risk_left[1]
    ricker_extrisk_d0$risk_right_d0[i]<-ss$risk_right[1]
}

@@

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  liness(s$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
  #---------------------------------------------------
  ## Allow a second plot on the same graph
  #par(new=TRUE)
